Generality in food webs scales with species richness but not with latitude

### 2015-06-18 manuscript/latitudepaper.tex
Tentative last paragraph of discussion

  Unlike species richness, only generality increased with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estaurine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).

@@

>>>>

  Unlike species richness, only generality showed an overall increase with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estaurine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).

@@

  The scaling of link density, generality and vulnerability with proportions
  of species at different trophic levels, however, did not differ between lakes
  and most other food webs. Indeed, there was comparatively little variation in
  scaling with the trophic-level breakdown of a web across ecosystem types.
  Terrestrial food webs tended to exhibit less change in scaling over latitude
  than other ecosystem types, as did marine webs when considering scaling with
  the proportion of basal resources. More excitingly, the negative relationships
  between the proportion of top predators in a web and link density and
  vulnerability were weaker (i.e., the scaling exponent was more strongly
  negative) in low-latitude stream ecosystems. This may imply that high-latitude
  top predators tend to be more generalist than their low-latitude equivalents.
  More generally, the lack of correspondence between the scaling of food-web
  properties with species richness and with proportions of species at each
  trophic level suggests that the size and trophic breakdowns of a community can
  provide different information about the breadth of niches in that community.
